Testing Quasar Unification with Clumpy Wind Models

### 2015-11-11 paper.tex
still updating

%% declare any packages used
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{color}
\usepackage{pdfpages}
\usepackage{appendix}
\usepackage{subfigure}
\usepackage{url}
%\usepackage{pngfig}
%\usepackage[dvips]{color}mak
%\usepackage{aabib}

@@

For this study, we use the MCRT code \py\ we have developed to carry out our 
radiative transfer and photoionization simulations in non-local thermodynamic
equilibrium (non-LTE). The code can be used to model a variety of
disc-wind systems; it has been used with application to accreting white dwarfs 
(Long \& Knigge 2002, hereafter LK02; Noebauer et al. 2010; 
Matthews et al. 2015, hereafter M15), young-stellar objects 
\citep{simmacro2005} and quasars/AGN (H13, H14).\nocite{noebauer, M15, LK02}

@@

Our approach to line transfer is based upon the macro-atom implementation developed by \cite{lucy2002, lucy2003}. In our case, for reasons of computational effieciency, we adopt the  hybrid macro-atom scheme 
described by M15 
%(an improvement over that used by H14 for our earlier quasar study), 
in which the energy flows
through the system are described in terms of indivisible
energy quanta of radiant or kinetic energy 
(`$r-$packets' and `$k-$packets' respectively; see also section 2.3).
These energy packets interact with either two-level `simple ions'
or full `macro-atoms'. 
Our scheme allows one to treat non-LTE line transfer in radiative equilibrium
without approximation for elements that are identified as 
full macro-atoms, while maintaining the fast `two-level' 
treatment of resonance lines when elements are identified 
as simple-ions (see M15). In this study,
only H is treated as a macro-atom, because 
we expect recombination to be important
in determining their level populations and resultant line emission, and because we were especially interested in the contribution to AGN spectra of \LA.  In H13, all atoms were treated in a two-level approximation.

@@

In order to calculate the photoionization rate, 
we model the SED in a grid cell using the technique described by H13. In this scheme,
the mean intensity, $J_{\nu}$ in a series of $n$ bands is modeled as either a power law or exponential
in frequency $\nu$, with the fit parameters deduced from band-limited radiation field estimators.
% \begin{equation}
% J_{\nu,i}=K_{pl}\nu^{\alpha_{pl}},
% \end{equation}
% for a band $i$, or an exponential 
% \begin{equation}
% J_{\nu,i}=K_{exp} e^{(-h\nu/k T_{exp})}.
% \end{equation}
% Here, $K_{exp}$, $K_{pl}$, $T_{exp}$ and $\alpha_{pl}$ are spectral fit parameters
% deduced from the band-limited radiation field estimators.
The ionization rate out of ion $j$ can then be written as 
\begin{equation}
R_{j,j+1}(J)= 
\displaystyle{
n_i \left(C_{j} n_e + 
\sum_{band~i=0}^{n}~
{\int_{\nu_i}^{~\nu_i+1} \frac{4 \pi J_{\nu,i}\sigma_j(\nu)}  {h \nu} d\nu}
\right),}
\end{equation}
where $\sigma_j$ is the photoionization cross-section, $n_e$
is the electron density and $C_{j}$
represents the collisional ionization coefficient.
The recombination rate {\em into} ion $j$ is given by 
\begin{equation}
R_{j+1,j}(T_e) = (\alpha^j_{RR} + \alpha^j_{CR}) n_{j+1} n_e,
\end{equation}
where each $\alpha^j$ here is the recombination rate coefficient into the ground state of ion $j$.
The subscripts denote radiative and 
collisional (three-body) recombination, respectively. 
$T_e$ is the electron temperature.
%% We neglect recombination to and from excited states in the simple-ion calculation. 
For simple-ions, we use a dilute Boltzmann equation to calculate 
the population of level $k$ in ionic stage $j$,
\begin{equation}
\frac{n_{jk}}{n_j} = \frac{W g_k}{z_j(T_R)} \exp(-E_k/kT_R).
\end{equation}
Here $z_j$ is the partition function of ionic stage $j$,
$T_R$ is the effective radiation temperature,
$E_k$ is the energy difference between level $k$ and the ground state,
and $g_k$ is the statistical weight of level $k$. 
We stress that this approximation is not required for ions
treated as macro-atoms.

@@

\subsection{Photon Sources}

The accretion disc in our model is geometrically thin, but optically thick.
We thus treat the disc as an ensemble of blackbodies with a 
\cite{shakurasunyaev1973} effective temperature profile. 
The emergent SED is then determined by the specified accretion rate ($\dot{m}$)
and central BH mass ($M_{BH}$).
All photon sources in our model are assumed to be opaque, meaning
that photons which strike them are destroyed.
The inner radius of the disc extends to the innermost 
stable circular orbit (ISCO) of the BH. 
We assume a Schwarzchild BH with an ISCO at $6~r_G$, where 
$r_G = GM_{BH}/c^2$ is the gravitational radius.
For a $10^9~M_\odot$ black hole, this is equal to $8.8\times10^{14}~{\rm cm}$ 
or $\sim10^{-4}~{\rm pc}$.

The X-ray source in our model is treated as an isotropic sphere at the ISCO,
which emits r-packets according to a power law in flux with index $\alpha_X$, of the form
\begin{equation}
F_X (\nu) = K \nu^{\alpha_X}.
\end{equation}
The normalisation, $K_X$ of this power law is such that it 
produces the specified 2-10~keV luminosity, $L_X$.
In addition to the disc and X-ray source, 
the wind is able to reprocess radiation. However, new 
photon packets are not produced in the wind (as in LK02). 
Instead, this reprocessing is dealt with by enforcing strict
radiative equilibrium ({\em modulo} adiabatic cooling; see section~2.3)
via an indivisible energy packet
constraint (see Lucy 2002, M15).

@@

\subsection{Clumping}

Our previous modelling efforts assumed a smooth outflow, 
in which the density at a given point was determined only by the 
kinematic parameters and mass loss rate. However, as already discussed,
AGN winds exhibit significant substructure -- the outflow is expected to be
{\em clumpy}, rather than smooth, and probably on a variety of scales. 
Implementing a treatment of clumping is challenging, for
two main reasons. First, there are significant 
computational difficulties associated with adequately
resolving and realistically modelling a series of small scale, high density
regions with a MCRT code. Second, the addition of multiple additional degrees of
freedom in the model results in significantly wider parameter space.
Unfortuantely, the physical scale lengths and density contrasts 
associated with these parameters cannot be well-constrained from observations.

To allow for clumping in our outflow we adopt a simple approximation
used extensively in stellar wind modelling, known as 
{\em microclumping} \citep{hamann1998}(MORE REFS). The key assumption here is that 
typical clump sizes are much smaller than the typical photon mean free path, 
and thus the clumps are 
both geometrically and optically thin. This approach 
allows one to introduce a `filling factor', $f$, which is the 
fraction of the volume of the plasma filled by clumps. The intra-clump
medium is assumed to be a vacuum. We can then introduce the 
density enhancement, $D$, which is defined as 
\begin{equation}
D = \frac{1}{f}.
\end{equation}
We then multiply all densities in the model by $D$, and all emitting volumes
by $f$. This has the effect of enhancing all emissivities and opacities
that scale with the square of density (such as collisional excitation and recombination) 
by a factor $D$. All processes that scale linearly with density 
(such as electron scattering and bound-free opacity)
will remain unchanged for a given ionization state.

Clumping the wind has an important effect on the ionization state and has
been proposed as a solution to the so-called `over-ionization problem' in 
disc winds (REFs). This is the main motivation for incorporating microclumping
into our model. This treatment is first-order; it does not adequately
represent the complex substructures and stratifications in ionization
state we expect in AGN outflows. Nevertheless, clumping is clearly
important in these flows, and this parameterization allows a simple estimate
for the effect clumping might have on the ionization state and emergent 
line emission. It is also encouraging that microclumping has been used 
successfully in fits to O-star wind spectra \citep{hillier1991eswingsmodel}.

@@

Using this prescription, we conducted a limited parameter
search over a 5-dimensional parameter space involving the 
variables $r_{min}$, $\theta_{min}$, $f$, $\alpha$ and $R_v$.
The grid points are shown in table 1.
The aim here was to first fix $M_{BH}$ and $\dot{m}$ to their H13 values,
and increase $L_X$ to $10^{45}$~erg~s$^{-1}$ (a more realistic value for a 
quasar of $10^9M_\odot$ and an eddington fraction of $0.2$; see section~\ref{sec:xray}). 
We then evaluated these models based on the following criteria:
\begin{itemize}
\item Does the model avoid over-ionization and thus produce strong BALs with $BI > ??$?
\item Does significant line emission emerge at low inclinations, with $EW\sim50\AA$ in \civ?
\item Do H recombination lines appear in the spectrum, $EW\sim50\AA$ in \la?
\item Do a certain range of angles produce LoBAL features?
\item Does the model compare favourably to quasar composite spectra?
\end{itemize}
We arrived at a model
In this section, we present one of the most promising models and discuss
the various successes and failures.
This allows us to gain insight into fundamental geometrical 
and physical constraints and assess the potential for unification. 
The full grid, including output synthetic spectra and plots can be found at
\url{jhmatthews.github.io/quasar-wind-grid/}.

\begin{table}
\begin{tabular}{p{2cm}p{1cm}p{1cm}p{1cm}p{1cm}}
Parameter & \multicolumn{4}{|l|}{Grid Point Values}  \\
\hline \hline 
$r_{min}$ 	&	 $6r_{g}$ & $60r_{g}$ & \multicolumn{2}{|l|}{$300r_{g}$} \\ 
$\theta_{min}$ 	&	 $40^{\circ}$ & $55^{\circ}$ & \multicolumn{2}{|l|}{$70^{\circ}$} \\ 
$R_v$  	        &	 $10^{18}$cm & \multicolumn{3}{|l|}{$10^{19}$cm} \\ 
$\alpha$ 	&	 $0.5$ & $0.6$ & $0.75$ & $1.5$ \\
$f$ 	&	 $0.01$ & $0.1$ & \multicolumn{2}{|l|}{$1$}  \\
\hline 
\end{tabular}
\caption{The grid points used in the parameter search.}
\label{grid_table}
\end{table}

@@

\begin{table}
\begin{tabular}{p{3cm}p{4cm}}
\hline Next-generation Model Parameters 	&	 Value \\ 
\hline \hline 
$M_{BH}$ 	 &	 $1\times 10^9~\rm{M_{\odot}}$ \\ 
$\dot{M}_{acc}$ 	 &	 $5~M_{\odot}yr^{-1} \simeq 0.2~\dot{M}_{Edd}$\\ 
$\alpha_X$ 	 &	 $-0.9$ \\ 
$L_{X} $ 	 &	 $10^{45}~\rm{ergs~s^{-1}}$$^*$ \\ 
$r_{disc}(min)=r_{X}$   &	 $6r_g=8.8\times10^{14}~{\rm cm}$ \\ 
$r_{disc}(max)$   &	 $3400r_g = 5\times10^{17}~{\rm cm}$ \\ 
$\dot{M}_{wind}$  &	 $5~M_{\odot}yr^{-1}$ \\ 
$r_{min}$ 	&	 $300r_{g} = 4.4\times10^{16}~{\rm cm}$\\ 
$r_{max}$ 	&	 $600r_{g} = 8.8\times10^{16}~{\rm cm}$ \\ 
$\theta_{min}$ 	&	 $70.0^{\circ}$ \\ 
$\theta_{max}$ 	&	 $82.0^{\circ}$ \\ 
$\lambda$ 	&	 $0$ \\ 
$v_{\infty}(r_0)$ 	&	 $v_{esc}(r_0)$ \\ 
$R_v$  	        &	 $10^{19}$cm$^*$ \\ 
$\alpha$ 	&	 $0.6^*$ \\
$f$ 	&	 $0.01^*$  \\
$n_x$ 	&	 $100$  \\
$n_z$ 	&	 $200$  \\
\hline 
% Derived Parameters 	&	 Value \\ 
% \hline \hline
% $L_{\nu}(2500\mbox{\scriptsize{\AA}})$&	 $6.3\times10^{30}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
% $L_{\nu}(2keV)$   &	 $1.2\times10^{25}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
% $L_{bol}$ 	 &	 $2.4\times10^{46}~\rm{ergs~s^{-1}}$\\
% $M_{bol}$ 	 &	 -27.4\\ 
% $M_u$            &	 -26.2\\ 
% $\alpha_{OX} $ 	 &	 -2.2\\ 
\end{tabular}
\caption{Wind geometry parameters used in the model.}
\label{wind_param}
\end{table}

@@

One common way to quantify the ionization state of a plasma
is through the ionization parameter, $U_H$, given by
\begin{equation}
U_H = \frac{4\pi}{n_H c}\int_{13.6{\rm{eV}}}^{\infty}\frac{{J_{\nu}d\nu}}{h\nu}.
\end{equation}
\noindent where $\rm{n_H}$ is the local number density of H, and $\nu$ denotes photon 
frequency. Shown in figure~\ref{fig:wind},
the ionization parameter is a useful measure of the global ionization state,
as it represents the ratio of the number density of 
H ionizing photons to the local H density.
It is, however, a poor representation of the 
ionization state of species such as \civ\ as it encodes no information
about the shape of the SED. In our case, the X-ray photons 
are dominant in the photoionization of the UV resonance line ions. 
This explains why a factor of 100 increase in X-ray luminosity requires
a clumping factor of 0.01, even though the value of $U_H$ decreases by only a factor of $\sim10$ 
compared to H13. This is also the reason for significant Lyman edge photoabsorption
at the highest inclinations (see section 4.3).

>>>>

%% declare any packages used
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{color}
\usepackage{pdfpages}
\usepackage{appendix}
\usepackage{subfigure}
\usepackage{url}
\usepackage{amsmath}
%\usepackage{pngfig}
%\usepackage[dvips]{color}mak
%\usepackage{aabib}

@@

For this study, we use the MCRT code \py\ we have developed to carry out our 
radiative transfer and photoionization simulations in non-local thermodynamic
equilibrium (non-LTE). The code can be model a variety of
disc-wind systems; it has been used with application to accreting white dwarfs 
(Long \& Knigge 2002, hereafter LK02; Noebauer et al. 2010; 
Matthews et al. 2015, hereafter M15), young-stellar objects 
\citep{simmacro2005} and quasars/AGN (H13, H14).\nocite{noebauer, M15, LK02}

@@

Our approach to line transfer is based upon the macro-atom implementation developed by 
\cite{lucy2002, lucy2003}, in which the energy flows through the system are described in 
terms of indivisible energy quanta of radiant or kinetic energy 
(`$r-$packets' and `$k-$packets' respectively; see also section~\ref{sec:photon_sources}). 
In our case, for reasons of computational efficiency, we adopt the  hybrid macro-atom scheme 
described by M15.
%(an improvement over that used by H14 for our earlier quasar study), 
In this scheme, the energy packets interact with either two-level `simple ions' 
or full `macro-atoms'. This allows one to treat non-LTE line transfer in radiative equilibrium
without approximation for elements that are identified as 
full macro-atoms, while maintaining the fast `two-level' 
treatment of resonance lines when elements are identified 
as simple-ions (see M15). In this study,
only H is treated as a macro-atom, because 
we expect recombination to be important
in determining their level populations and resultant line emission, and because we were especially interested in the contribution to AGN spectra of \LA.  
H13 treated all atoms in a two-level approximation.

@@

In order to calculate the photoionization rate, 
we model the SED in a grid cell using the technique described by H13. In this scheme,
the mean intensity, $J_{\nu}$ in a series of $n$ bands is modeled as either a power law or exponential
in frequency $\nu$, with the fit parameters deduced from band-limited radiation field estimators.
% \begin{equation}
% J_{\nu,i}=K_{pl}\nu^{\alpha_{pl}},
% \end{equation}
% for a band $i$, or an exponential 
% \begin{equation}
% J_{\nu,i}=K_{exp} e^{(-h\nu/k T_{exp})}.
% \end{equation}
% Here, $K_{exp}$, $K_{pl}$, $T_{exp}$ and $\alpha_{pl}$ are spectral fit parameters
% deduced from the band-limited radiation field estimators.
The ionization rate out of ion $j$ can then be written as 
\begin{equation}
R_{j,j+1}(J)= 
\displaystyle{
n_j \left(C_{j} n_e + 
\sum_{band~i=0}^{n}~
{\int_{\nu_i}^{~\nu_i+1} \frac{4 \pi J_{\nu,i}\sigma_j(\nu)}  {h \nu} d\nu}
\right),}
\end{equation}
where $\sigma_j$ is the photoionization cross-section, $n_e$
is the electron density and $C_{j}$
represents the collisional ionization coefficient.
The recombination rate {\em into} ion $j$ is given by 
\begin{equation}
R_{j+1,j}(T_e) = (\alpha^j_{RR} + \alpha^j_{CR}) n_{j+1} n_e,
\end{equation}
where each $\alpha^j$ here is the recombination rate coefficient into the ground state of ion $j$.
The subscripts denote radiative and 
collisional (three-body) recombination, respectively. 
$T_e$ is the electron temperature.
%% We neglect recombination to and from excited states in the simple-ion calculation. 
For simple-ions, we use a dilute Boltzmann equation to calculate 
the population of level $k$ in ionic stage $j$,
\begin{equation}
\frac{n_{jk}}{n_j} = \frac{W g_k}{z_j(T_R)} \exp(-E_k/kT_R).
\end{equation}
Here $z_j$ is the partition function of ionic stage $j$,
$T_R$ is the effective radiation temperature,
$E_k$ is the energy difference between level $k$ and the ground state,
and $g_k$ is the statistical weight of level $k$. 
We stress that this approximation is not required for ions
treated as macro-atoms.

@@

\subsection{Photon Sources}
\label{sec:photon_sources}

We include two sources of r-packets in our model:
An accretion disc and central X-ray source.
The accretion disc is assumed to be geometrically thin, but optically thick.
We thus treat the disc as an ensemble of blackbodies with a 
\cite{shakurasunyaev1973} effective temperature profile. 
The emergent SED is then determined by the specified accretion rate ($\dot{m}$)
and central BH mass ($M_{BH}$).
All photon sources in our model are opaque, meaning
that r-packets which strike them are destroyed.
The inner radius of the disc extends to the innermost 
stable circular orbit (ISCO) of the BH. 
We assume a Schwarzchild BH with an ISCO at $6~r_G$, where 
$r_G = GM_{BH}/c^2$ is the gravitational radius.
For a $10^9~M_\odot$ black hole, this is equal to $8.8\times10^{14}~{\rm cm}$ 
or $\sim10^{-4}~{\rm pc}$.

The X-ray source is treated as an isotropic sphere at the ISCO,
which emits r-packets according to a power law in flux with index $\alpha_X$, of the form
\begin{equation}
F_X (\nu) = K_X \nu^{\alpha_X}.
\end{equation}
The normalisation, $K_X$ of this power law is such that it 
produces the specified 2-10~keV luminosity, $L_X$.
In addition to the disc and X-ray source, 
the wind is able to reprocess radiation. However, new 
photon packets are not produced in the wind (as in LK02). 
Instead, this reprocessing is dealt with by enforcing strict
radiative equilibrium ({\em modulo} adiabatic cooling; see section~2.3)
via an indivisible energy packet
constraint (see Lucy 2002, M15).

@@

\subsection{A First Approximation for Clumping}

Our previous modelling efforts assumed a smooth outflow, 
in which the density at a given point was determined only by the 
kinematic parameters and mass loss rate. However, as already discussed,
AGN winds exhibit significant substructure -- the outflow is expected to be
{\em clumpy}, rather than smooth, and probably on a variety of scales. 
Implementing a treatment of clumping is challenging, for
two main reasons. First, there are significant 
computational difficulties associated with adequately
resolving and realistically modelling a series of small scale, high density
regions with a MCRT code. Second, the addition of multiple additional degrees of
freedom in the model results in significantly wider parameter space.
Unfortunately, the physical scale lengths and density contrasts 
associated with these parameters cannot be well-constrained from observations.

To allow for clumping in our outflow we adopt a simple approximation
used successfully in stellar wind modelling, known as 
{\em microclumping} \citep{hamann1998,hamann2008}(MORE REFS). 
The key assumption is that typical clump sizes are much smaller than the 
typical photon mean free path, and thus the clumps are 
both geometrically and optically thin. This approach 
allows one to introduce a `volume filling factor', $f_V$. 
The intra-clump medium is assumed to be a vacuum, so the 
density of the clumps is then multiplied by the ``density enhancement'' 
$D=1/f_V$. Opacities, $\kappa$, and emissivities, $\epsilon$, 
can then be expressed as

% \begin{subequations}
% \begin{align}
%         \kappa &= f_V \kappa_C(D) \\
%         \epsilon &= f_V \epsilon_C(D)
% \end{align}
% \end{subequations}
\begin{equation}
\kappa = f_V \kappa_C(D);~~\epsilon = f_V \epsilon_C(D).
\end{equation}
% \kappa = f_V \kappa_C(D) && \epsilon = f_V \epsilon_C(D).
% \end{equation}
Here the subscript $C$ denotes that the quantity is calculated using the 
enhanced density in the clump. The resultant effect is that {\em linear} processes,
such as electron scattering, are unchanged, as $f_V$ and $D$ will cancel out. 
However, any quantity which scales with the {\em square} of density, 
such as collisional excitation or recombination, will increase by a factor of $D$.

% which is defined as 
% \begin{equation}
% D = \frac{1}{f} && 
% \end{equation}
% We then multiply all densities in the model by $D$, and all emitting volumes
% by $f$. This has the effect of enhancing all emissivities and opacities
% that scale with the square of density (such as collisional excitation and recombination) 
% by a factor $D$. All processes that scale linearly with density 
% (such as electron scattering and bound-free opacity)
% will remain unchanged for a given ionization state.

Clumping the wind has an important effect on the ionization state and has
been proposed as a solution to the so-called `over-ionization problem' in 
disc winds \citep{hamann2013}. This is the main motivation for incorporating microclumping
into our model. This treatment is first-order; it does not adequately
represent the complex substructures and stratifications in ionization
state we expect in AGN outflows. Nevertheless, clumping is clearly
important in these flows, and this parameterization allows a simple estimate
for the effect clumping might have on the ionization state and emergent 
line emission. 
% It is also encouraging that microclumping has been used 
% successfully in fits to O-star wind spectra \citep{hillier1991eswingsmodel}.

@@

Using this prescription, we conducted a limited parameter
search over a 5-dimensional parameter space involving the 
variables $r_{min}$, $\theta_{min}$, $f_V$, $\alpha$ and $R_v$.
The grid points are shown in table 1.
The aim here was to first fix $M_{BH}$ and $\dot{m}$ to their H13 values,
and increase $L_X$ to $10^{45}$~erg~s$^{-1}$ (a more realistic value for a 
quasar of $10^9M_\odot$ and an eddington fraction of $0.2$; see section~\ref{sec:xray}). 
We then evaluated these models based on the following criteria:
\begin{itemize}
\item Does the model avoid over-ionization and thus produce strong BALs with $BI > ??$?
\item Does significant line emission emerge at low inclinations, with $EW\sim50\AA$ in \civ?
\item Do H recombination lines appear in the spectrum, $EW\sim50\AA$ in \la?
\item Do a certain range of angles produce LoBAL features?
\item Does the model compare favourably to quasar composite spectra?
\end{itemize}
In this section, we present one of the most promising models and discuss
the various successes and failures with respect to the above criteria.
This allows us to gain insight into fundamental geometrical 
and physical constraints and assess the potential for unification. 
The full grid, including output synthetic spectra and plots can be found at
\url{jhmatthews.github.io/quasar-wind-grid/}.

\begin{table}
\begin{tabular}{p{2cm}p{1cm}p{1cm}p{1cm}p{1cm}}
Parameter & \multicolumn{4}{|l|}{Grid Point Values}  \\
\hline \hline 
$r_{min}$ 	&	 $6r_{g}$ & $60r_{g}$ & \multicolumn{2}{|l|}{$300r_{g}$} \\ 
$\theta_{min}$ 	&	 $40^{\circ}$ & $55^{\circ}$ & \multicolumn{2}{|l|}{$70^{\circ}$} \\ 
$R_v$  	        &	 $10^{18}$cm & \multicolumn{3}{|l|}{$10^{19}$cm} \\ 
$\alpha$ 	&	 $0.5$ & $0.6$ & $0.75$ & $1.5$ \\
$f_V$ 	&	 $0.01$ & $0.1$ & \multicolumn{2}{|l|}{$1$}  \\
\hline 
\end{tabular}
\caption{The grid points used in the parameter search.}
\label{grid_table}
\end{table}

@@

\begin{table}
\begin{tabular}{p{3cm}p{4cm}}
\hline Next-generation Model Parameters 	&	 Value \\ 
\hline \hline 
$M_{BH}$ 	 &	 $1\times 10^9~\rm{M_{\odot}}$ \\ 
$\dot{M}_{acc}$ 	 &	 $5~M_{\odot}yr^{-1} \simeq 0.2~\dot{M}_{Edd}$\\ 
$\alpha_X$ 	 &	 $-0.9$ \\ 
$L_{X} $ 	 &	 $10^{45}~\rm{ergs~s^{-1}}$$^*$ \\ 
$r_{disc}(min)=r_{X}$   &	 $6r_g=8.8\times10^{14}~{\rm cm}$ \\ 
$r_{disc}(max)$   &	 $3400r_g = 5\times10^{17}~{\rm cm}$ \\ 
$\dot{M}_{wind}$  &	 $5~M_{\odot}yr^{-1}$ \\ 
$r_{min}$ 	&	 $300r_{g} = 4.4\times10^{16}~{\rm cm}$\\ 
$r_{max}$ 	&	 $600r_{g} = 8.8\times10^{16}~{\rm cm}$ \\ 
$\theta_{min}$ 	&	 $70.0^{\circ}$ \\ 
$\theta_{max}$ 	&	 $82.0^{\circ}$ \\ 
$\lambda$ 	&	 $0$ \\ 
$v_{\infty}(r_0)$ 	&	 $v_{esc}(r_0)$ \\ 
$R_v$  	        &	 $10^{19}$cm$^*$ \\ 
$\alpha$ 	&	 $0.6^*$ \\
$f_V$ 	&	 $0.01^*$  \\
$n_x$ 	&	 $100$  \\
$n_z$ 	&	 $200$  \\
\hline 
% Derived Parameters 	&	 Value \\ 
% \hline \hline
% $L_{\nu}(2500\mbox{\scriptsize{\AA}})$&	 $6.3\times10^{30}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
% $L_{\nu}(2keV)$   &	 $1.2\times10^{25}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
% $L_{bol}$ 	 &	 $2.4\times10^{46}~\rm{ergs~s^{-1}}$\\
% $M_{bol}$ 	 &	 -27.4\\ 
% $M_u$            &	 -26.2\\ 
% $\alpha_{OX} $ 	 &	 -2.2\\ 
\end{tabular}
\caption{Wind geometry parameters used in the model.}
\label{wind_param}
\end{table}

@@

One common way to quantify the ionization state of a plasma
is through the ionization parameter, $U_H$, given by
\begin{equation}
U_H = \frac{4\pi}{n_H c}\int_{13.6{\rm{eV}}}^{\infty}\frac{{J_{\nu}d\nu}}{h\nu}.
\end{equation}
\noindent where $\rm{n_H}$ is the local number density of H, and $\nu$ denotes photon 
frequency. Shown in figure~\ref{fig:wind},
the ionization parameter is a useful measure of the global ionization state,
as it represents the ratio of the number density of 
H ionizing photons to the local H density.
It is, however, a poor representation of the 
ionization state of species such as \civ\ as it encodes no information
about the shape of the SED. In our case, the X-ray photons 
are dominant in the photoionization of the UV resonance line ions. 
This explains why a factor of 100 increase in X-ray luminosity requires
a clumping factor of 0.01, even though the value of $U_H$ decreases by only a factor of $\sim10$ 
compared to H13. 
%This is also the reason for significant Lyman edge photoabsorption
%at the highest inclinations (see section 4.3).

### 2015-11-11 paper_mnras.tex
still updating

Using this prescription, we conducted a limited parameter
search over a 5-dimensional parameter space involving the 
variables $r_{min}$, $\theta_{min}$, $f$, $\alpha$ and $R_v$.
The grid points are shown in table 1.
The aim here was to first fix $M_{BH}$ and $\dot{m}$ to their H13 values,
and increase $L_X$ to $10^{45}$~erg~s$^{-1}$ (a more realistic value for a 
quasar of $10^9M_\odot$ and an eddington fraction of $0.2$; see section~\ref{sec:xray}). 
We then evaluated these models based on the following criteria:
\begin{itemize}
\item Does the model avoid over-ionization and thus produce strong BALs with $BI > ??$?
\item Does significant line emission emerge at low inclinations, with $EW\sim50\AA$ in \civ?
\item Do H recombination lines appear in the spectrum, $EW\sim50\AA$ in \la?
\item Do a certain range of angles produce LoBAL features?
\item Does the model compare favourably to quasar composite spectra?
\end{itemize}
We arrived at a model
In this section, we present one of the most promising models and discuss
the various successes and failures.
This allows us to gain insight into fundamental geometrical 
and physical constraints and assess the potential for unification. 
The full grid, including output synthetic spectra and plots can be found at
\url{jhmatthews.github.io/quasar-wind-grid/}.

\begin{table}
\begin{tabular}{p{2cm}p{1cm}p{1cm}p{1cm}p{1cm}}
Parameter & \multicolumn{4}{|l|}{Grid Point Values}  \\
\hline \hline 
$r_{min}$ 	&	 $6r_{g}$ & $60r_{g}$ & \multicolumn{2}{|l|}{$300r_{g}$} \\ 
$\theta_{min}$ 	&	 $40^{\circ}$ & $55^{\circ}$ & \multicolumn{2}{|l|}{$70^{\circ}$} \\ 
$R_v$  	        &	 $10^{18}$cm & \multicolumn{3}{|l|}{$10^{19}$cm} \\ 
$\alpha$ 	&	 $0.5$ & $0.6$ & $0.75$ & $1.5$ \\
$f$ 	&	 $0.01$ & $0.1$ & \multicolumn{2}{|l|}{$1$}  \\
\hline 
\end{tabular}
\caption{The grid points used in the parameter search.}
\label{grid_table}
\end{table}

>>>>

Using this prescription, we conducted a limited parameter
search over a 5-dimensional parameter space involving the 
variables $r_{min}$, $\theta_{min}$, $f_V$, $\alpha$ and $R_v$.
The grid points are shown in table 1.
The aim here was to first fix $M_{BH}$ and $\dot{m}$ to their H13 values,
and increase $L_X$ to $10^{45}$~erg~s$^{-1}$ (a more realistic value for a 
quasar of $10^9M_\odot$ and an eddington fraction of $0.2$; see section~\ref{sec:xray}). 
We then evaluated these models based on the following criteria:
\begin{itemize}
\item Does the model avoid over-ionization and thus produce strong BALs with $BI > ??$?
\item Does significant line emission emerge at low inclinations, with $EW\sim50\AA$ in \civ?
\item Do H recombination lines appear in the spectrum, $EW\sim50\AA$ in \la?
\item Do a certain range of angles produce LoBAL features?
\item Does the model compare favourably to quasar composite spectra?
\end{itemize}
In this section, we present one of the most promising models and discuss
the various successes and failures.
This allows us to gain insight into fundamental geometrical 
and physical constraints and assess the potential for unification. 
The full grid, including output synthetic spectra and plots can be found at
\url{jhmatthews.github.io/quasar-wind-grid/}.

\begin{table}
\begin{tabular}{p{2cm}p{1cm}p{1cm}p{1cm}p{1cm}}
Parameter & \multicolumn{4}{|l|}{Grid Point Values}  \\
\hline \hline 
$r_{min}$ 	&	 $6r_{g}$ & $60r_{g}$ & \multicolumn{2}{|l|}{$300r_{g}$} \\ 
$\theta_{min}$ 	&	 $40^{\circ}$ & $55^{\circ}$ & \multicolumn{2}{|l|}{$70^{\circ}$} \\ 
$R_v$  	        &	 $10^{18}$cm & \multicolumn{3}{|l|}{$10^{19}$cm} \\ 
$\alpha$ 	&	 $0.5$ & $0.6$ & $0.75$ & $1.5$ \\
$f_V$ 	&	 $0.01$ & $0.1$ & \multicolumn{2}{|l|}{$1$}  \\
\hline 
\end{tabular}
\caption{The grid points used in the parameter search.}
\label{grid_table}
\end{table}
